\documentclass[letterpaper,12pt]{article}

\input{worksheet-preamble}
%\renewcommand{\week}{Week 13}

\begin{document}

\begin{enumerate}
\setlength\itemsep{3.5 in}

\item 
Express the wave function for one-dimensional harmonic waves in terms of the following parameters:
\begin{itemize}
	\item Frequency and wavelength
	\item Period and wavelength
	\item Angular frequency and wave vector
\end{itemize}

\item Consider the plane electromagnetic wave in vacuum (in SI units)
given by the expressions: \\$E_x = 0$ \\$E_y = 4 \cos [2p * 10^{14} (t - x/c) + p/2]$\\ $E_z = 0$
\begin{itemize}
	\item Calculate the frequency, wavelength, direction of motion, amplitude, initial phase angle, and polarization of the wave.
	\item Write an expression for the magnetic flux density.
\end{itemize}

\item Write an expression for the $\vec{E}$ and $\vec{B}$ fields that constitute a plane
harmonic wave traveling in the $+z$-direction. The wave is linearly polarized with its plane of vibration at 45° to the $yz$-plane.

\item A 500-nm harmonic EM wave, whose electric field is in the z-direction, is traveling in the y-direction in vacuum. 
\begin{itemize}
	\item What is the frequency of the wave?
	\item Determine both v and k for this wave.
	\item If the electric field amplitude is 700 V/m, what is the amplitude of the magnetic field?
	\item Write an expression for both $E(t)$ and $B(t)$ given that each is zero at $x = 0$ and $t = 0$. Put in all the appropriate units.
\end{itemize}

\item 
Consider a linearly polarized plane electromagnetic wave traveling in the $+x$-direction in free space having as its plane of vibration the $xy$-plane. Given that its frequency is \SI{5}{\mega\hertz} and its amplitude is $E_0 = \SI{0.05}{V/m}$
\begin{itemize}
	\item Find the period and wavelength of the wave.
	\item Write an expression for $E(t)$ and $B(t)$.
	\item Find the flux density, $<S>$, of the wave.
\end{itemize}

\item 
A light wave travels from point A to point B in vacuum. Suppose we introduce into its path a flat glass plate ($n = 1.50$) of thickness $L = \SI{1.00}{mm}$. If the vacuum wavelength is \SI{500}{nm}, how many waves span the space from A to B with and without the glass in place? What phase shift is introduced with the insertion of the plate?

\end{enumerate}

\newpage 

\ % The empty page

\newpage

\end{document}
